---
title: "GC- Final Project"
author: "George Cruz"
date: "7/23/2020"
output: html_document
---
# Final Project 
## In The Nature of Vocabulary Acquisition, Robert J. Sternberg of Yale University made a profound statement:
###“… vocabulary is probably the best single indicator of a person’s overall level of intelligence. Stated in another way, if one wants a quick and not-too-dirty measure of a person’s psychometrically measured intelligence, and thus has time to give just one brief test of it, vocabulary is generally the best predictor of overall score on a psychometric IQ test. (p. 90)”
###The purpose of my analysis will be to compare and contrast results from a vocabulary test conducted between 1974 and 2012 to try to understand the relationship between education/language accross these decades. 

```{r}
require(ggplot2)
theURL <- "https://raw.githubusercontent.com/georg4re/LearningR/master/Vocab.csv"
vocab <- read.table(file=theURL, header=TRUE, sep=",")
str(vocab)
summary(vocab)

```
### Rename some columns.
```{r}
library(dplyr)
newVocab <- rename(vocab, gender=sex, academic_level=education, lexicon=vocabulary)
head(newVocab)

```
### Looking at Level of education by gender.

```{r}
require(ggplot2)
library(dplyr)
library(magrittr)
# Create a group-means data set
gd <- (newVocab %>% group_by(year, gender) %>% summarize(level=mean(academic_level), lexicon=mean(lexicon)))

# Plot both data sets
#ggplot(data = gd, aes(x = year, y = level))+
#  geom_line(aes(color = gender), size = 2) +
#  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
ggplot(gd, aes(x = year, y = level)) + 
  geom_line(aes(color = gender), size = 1) +
  scale_color_manual(values = c("#E7B800", "#00008b")) +
  theme_minimal()

```

### Vocabulary Mastery by gender
```{r}
ggplot(gd, aes(x = year, y = lexicon)) + 
  geom_line(aes(color = gender), size = 1) +
  scale_color_manual(values = c("#E7B800", "#00008b")) +
  theme_minimal()

```

### Let's look at the data without regards to gender
```{r}
gd <- (newVocab %>% group_by(year) %>% summarize(level=mean(academic_level), lexicon=mean(lexicon)))

# Plot both data sets
#ggplot(data = gd, aes(x = year, y = level))+
#  geom_line(aes(color = gender), size = 2) +
#  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
ggplot(gd, aes(x = year, y = lexicon)) + 
  geom_line(color = "#7EF9FF", size = 1) +
  geom_line(aes(y=level), colour="orange") +
  theme_minimal()

```
