---
title: "GC- HW2"
author: "George Cruz"
date: "7/23/2020"
output: html_document
---
### Use the summary function to gain an overview of the data set. Then display the mean and median for at least two attributes.

```{r}
library(magrittr)
library(dplyr)
theURL <- "https://raw.githubusercontent.com/georg4re/LearningR/master/Vocab.csv"
vocab <- read.table(file=theURL, header=TRUE, sep=",")

vocab %>% group_by(year, sex) %>% summarize(mean(education), mean(vocabulary), median(education), median(vocabulary))

```
### Create a new data frame with a subset of the columns and rows. Make sure to rename it.
```{r}
collegeDf = subset(vocab, education>12 )

df <- as_tibble(collegeDf) #To print nicely on Knit
print(df)

```



### Create new column names for the new data frame.

```{r newCollegeDF, max.print=30}
library(dplyr)
newCollegeDF <- rename(collegeDf, gender=sex, academic_level=education, lexicon=vocabulary)

df <- as_tibble(newCollegeDF) #To print nicely on Knit
print(df)
```

### Use the summary function to create an overview of your new data frame.
### Then print the mean and median for the same two attributes. Please compare.
```{r}
(newCollegeDF %>% group_by(year, gender) %>% summarize(mean(academic_level), mean(lexicon), median(academic_level), median(lexicon)))

```

### For at least 3 values in a column please rename so that every value in that column is renamed.

### Display enough rows to see examples of all of steps 1-5 above.
```{r}
newCollegeDF = mutate(newCollegeDF, gender = ifelse(gender == "Female", "F", "M"))
newCollegeDF = mutate(newCollegeDF, academic_level = ifelse(academic_level <= 14, "2 Year College", ifelse(academic_level <= 16, "Undergraduate", "Graduate")))

newCollegeDF <- as_tibble(newCollegeDF)
print(newCollegeDF)

```
